### 2014-10-28 LongDataResearchNotes/ARModel.Rmd
Created new dataframe with the lagged values.

>>>>

#create a date only variable not date time
LongWtrends$DateOnly<-as.Date(LongWtrends$Date)

library(sqldf)

#used to merge on the lagged values
CopyLong<-LongWtrends

LagFormData<-sqldf("select  LongWtrends.DateOnly, LongWtrends.hour, LongWtrends.F, LongWtrends.HE, CopyLong.F as LagF, CopyLong.HE as LagHE, LongWtrends.Weather, CopyLong.Weather as LagWeather  from LongWtrends,CopyLong where LongWtrends.DateOnly=(CopyLong.DateOnly-7) and LongWtrends.hour=CopyLong.hour;   ")
